Hierarchical time series forecasting in Emergency Medical Services

### 2022-11-16 manuscript/03-experiment.qmd
Removed stray character
Updating sec 3

The dataset used in this study is from a major ambulance service trust in Great Britain. It contains information relating to the daily number of attended incidents from 10 October 2015 to 31 July 2019 by nature of incidents, priority, the health board managing the service and the control area (or region). Figure @fig-hierarchy depicts both the hierarchical and grouped structure of the data. Figure @fig-hierarchy-1 illustrates the nested hierarchical structure based on control area and health board and Figure @fig-hierarchy-2 shows the grouped structure by priority and the nature of incident.

@@

Table @tbl-hierarchy also displays the structure of data with the total number of series at each level. At the top level, we have the total attended incidents for the country. We can split these total attended incidents by control area, by health board, by priority or by nature of incident. There are 3 control areas breakdown by 7 local health boards. Attended incident data are categorized into 3 priority classes of red, amber and green. There are also 35 different nature of incidents such as chest pain, stroke, breathing problem, etc. In total, across all levels of disaggregation, there are 1530 time series.

@@

Given the total number of time series, direct visual analysis is infeasible. Therefore, we first compute features of all 1530 time series and display the strength of trend and weekly seasonality strength in Figure @fig-feature. Each point represents one time series with the strength of trend in x-axis and the strength of seasonality in y-axis. It is clear that there are some series showing strong trends and/or seasonality, corresponding to series at the higher levels of the hierarchy. The majority of series show low trend and seasonality. These are time series belonging to the bottom series, series related to the nature of incidents for a given control, health board and priority level. Bottom series are dominated by noise with little or no systematic patterns.

@@

In addition to displaying the trend and seasonality features, we also visualize few time series at various levels of the aggregation. Figure @fig-dataviz2 reveals different information such as trend, seasonality and noise. For example, some series depict seasonality and trend, whereas some other series report low volume of attended incidents and entropy, making them more volatile and difficult to forecast. At the level on nature of incidents combined with categories of other levels, there are many series that contain zeros with low counts. As such, the data set represents a diverse set of daily time series patterns.

@@

**Naive:** We start with one of the simplest forecasting approaches used in practice - assuming that in the next few days, everything will be the same as similar days in the past. This is called "Naïve". In our case, given that we need a distribution of values, we will use a modified approach, where the empirical distribution of the daily attended incidents time series is used to forecast the future attended incidents distribution. We consider the empirical distribution of the most recent year of historic data on a rolling basis to capture potential changes in behavior over time.

@@

Despite the popularity and the relevance of automatic `ETS` in this study, however it may produce forecasts that are non-integer and negative. However, the number of attended incidents is an integer and non-negative. When using `ETS` , a time series transformation approach could be used to generate strictly positive forecasts, however forecasts are still not integer. An alternative is to use  forecasting models that produce integer, non-negative forecasts. in the following section we present Generalized Linear Models (GLMs) and Poisson Regression to produce count base forecasts.

**Generalized Linear Model (GLM): ** GLMs are a family of models developed to extend the concept of linear regression models. They perform a regression by modeling the response variable as coming from a particular member of the exponential family, and then transforming the mean of the response so that the transformed mean is a linear function of the predictors. One of the models that is frequently used in practice to generate count forecasts is the Poisson regression. We will consider forecasting attended incidents using the covariates spline trend,  day of the week dummy variables (from Monday to Sunday), Fourier terms to capture yearly seasonality, public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). We fit a Poisson regression model using the function `glm()` from the package in R, with the argument `family = poisson` to specify that we wish to fit a Poisson regression model.

**Poisson Regression using tscount: ** We consider another Poisson regression model that takes into account serial dependence in addition to covariates used in the GLM model. To that end, we use `tsglm()` function in _tscount_ package in R to model the attended incidents. The logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive. This model can be estimated via maximization of the likelihood function based on Poisson mass function. The regression model captures the short range serial dependence by including the three order autoregressive terms.

**Ensemble method:** we also use an ensemble method that combines forecasts generated from Naive, ETS, GLM and Poisson regression together to make more accurate forecasts than any individual
model.

@@

The data is spitted into training (up until 2018-07-31) and test (from  2018-08-01 to the end) sets, with all model development and hyper-parameter tuning performed using training data only. The time series cross validation is performed with a forecast horizon of $2*42$ days and advances in 42-day steps. Forecasting performance is evaluated using both point and probabilistic error measures. Forecast error is calculated by considering only the last 42 days and not the entire $2*42$ days. This corresponds on how forecasts are generated for planning in practice. Forecasting performance is evaluated using both point and probabilistic error measures. The point forecast accuracy is measured via Root Mean Squared Scaled Error (RMSSE) and Mean Absolute Scaled Error (MASE) that are describes below:

$$
RMSSE = \sqrt{mean(q_{j}^2)},
$$ {#eq-RMSSE}

where,

$$
q^2_{j} = \frac{ e^2_{j}}
    {\frac{1}{T-m}\sum_{t=m+1}^T (y_{t}-y_{t-m})^2},
$$
$e_{j}$ is the point forecast error $j$ and $m = 1$ for non-seasonal series and $m = 7$ for daily seasonal series, $y_t$ is the observation for period $t$ and $T$ is the sample size (observations used for training the forecasting model). Smaller RMSSE values suggest more accurate forecasts. Note that the measure is scale-independent, thus allowing us to average the results across series.

Mean Absolute Scaled Error (MASE) is calculated as:

$$
MASE = mean(|q_{j}|),
$$

where,
$$
q_{j} = \frac{ e_{j}}
    {\frac{1}{T-m}\sum_{t=m+1}^T |y_{t}-y_{t-m}|}.
$$

The denominator is the mean absolute error of the naive method in the fitting sample of $n$ observations and is used to scale the error.

To measure the forecast distribution performance, we calculate  the Continuous Rank Probability Score [@gneiting2014probabilistic]. It rewards sharpness and penalizes miscalibration, so it measures overall performance.

$$
CRPS=\frac{1}{h} \sum_{j=1}^{h} \int_{-\infty}^{\infty} \left(F^f_j(x) - F^0_j(x)\right)^2dx
$$ {#eq-CRPS}

where $F^f_j(x)$ is the forecasted Cumulative Density Function (CDF) of period $j$ and 𝐹$F^0_j(x)$ is the true CDF of period $j$.

>>>>

The dataset used in this study is from a major ambulance service trust in Great Britain. It contains information relating to the daily number of attended incidents from 1 October 2015 to 31 July 2019, disaggregated by nature of incidents, priority, the health board managing the service and the control area (or region). @fig-hierarchy depicts both the hierarchical and grouped structure of the data. @fig-hierarchy-1 illustrates the nested hierarchical structure based on control area and health board and @fig-hierarchy-2 shows the grouped structure by priority and the nature of incident.

@@

@tbl-hierarchy also displays the structure of data with the total number of series at each level. At the top level, we have the total attended incidents for the country. We can split these total attended incidents by control area, by health board, by priority or by nature of incident. There are 3 control areas breakdown by 7 local health boards. Attended incident data are categorized into 3 priority classes of red, amber and green. There are also 35 different nature of incidents such as chest pain, stroke, breathing problem, etc. In total, across all levels of disaggregation, there are 1530 time series.

@@

Given the total number of time series, direct visual analysis is infeasible. Therefore, we first compute features of all 1530 time series [@m3pca] and display the strength of trend and weekly seasonality strength in @fig-feature. Each point represents one time series with the strength of trend in x-axis and the strength of seasonality in y-axis. It is clear that there are some series showing strong trends and/or seasonality, corresponding to series at the higher levels of the hierarchy. The majority of series show low trend and seasonality. These are time series belonging to the bottom series, series related to the nature of incidents for a given control, health board and priority level. Bottom series are dominated by noise with little or no systematic patterns.

@@

In addition to displaying the trend and seasonality features, we also visualize few time series at various levels of the aggregation. @fig-dataviz2 reveals different information such as trend, seasonality and noise. For example, some series depict seasonality and trend, whereas some other series report low volume of attended incidents and entropy, making them more volatile and difficult to forecast. At the level on nature of incidents combined with categories of other levels, there are many series that contain zeros with low counts. As such, the data set represents a diverse set of daily time series patterns.

@@

**Naive:** We start with a simple forecasting approach, assuming that the future days will be similar to past days. We use the empirical distribution of the past daily attended incidents to create the forecast distribution of future attended incidents. We consider the empirical distribution of the most recent year of historic data on a rolling basis to capture potential changes in behavior over time.\todo{Actually we use all the data.}

@@

Despite the popularity and the relevance of automatic `ETS` in this study, however it may produce forecast distributions that are non-integer and include negative values, despite the number of attended incidents being integer and non-negative. When using `ETS`, a time series transformation approach could be used to generate strictly positive forecasts, although forecast distributions will still be non-integer. An alternative is to use  forecasting models that produce integer, non-negative forecasts. in the following section we present Generalized Linear Models (GLMs) and Poisson Regression to produce count base forecasts.

**Generalized Linear Model (GLM):** GLMs are a family of models developed to extend the concept of linear regression models. They perform a regression by modeling the response variable as coming from a particular member of the exponential family, and then transforming the mean of the response so that the transformed mean is a linear function of the predictors. One of the models that is frequently used in practice to generate count forecasts is the Poisson regression. We will consider forecasting attended incidents using the covariates spline trend,  day of the week dummy variables (from Monday to Sunday), Fourier terms to capture yearly seasonality, public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). We fit a Poisson regression model using the function `glm()` from the package in R, with the argument `family = poisson` to specify that we wish to fit a Poisson regression model.

**Poisson Regression using tscount:** We consider another Poisson regression model that takes into account serial dependence in addition to covariates used in the GLM model. To that end, we use `tsglm()` function in _tscount_ package in R to model the attended incidents. The logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive. This model can be estimated via maximization of the likelihood function based on Poisson mass function. The regression model captures the short range serial dependence by including the three order autoregressive terms.

**Ensemble method:** we also use an ensemble method that combines forecasts generated from Naive, ETS, GLM and Poisson regression to form a mixture distribution [@combinations].

@@

To evaluate the performance of the various forecasting approaches, we split the data into a series of ten training and test sets. We use a time series cross-validation approach [@hyndman2021forecasting], with a forecast horizon of 84 days, and each training set expanding in 42-day steps. The first training set uses all data up to 2018-04-25, and the first test set uses the 84 days beginning 2018-04-26. The second training set uses all data up to 2018-06-06, with the second test set using the following 84 days. The largest training set ends on 2019-05-09, with the test set ending on 2019-07-31. Model development and hyper-parameter tuning is performed using the training data only. Forecasting performance is evaluated using both point and probabilistic error measures. While we compute forecast errors for the entire 12 weeks, we are most interested in the last 42 days of each test set, because that corresponds to  how forecasts are generated for planning in practice. Forecasting performance is evaluated using both point and probabilistic error measures.

Point forecast accuracy is measured via the Mean Squared Scaled Error (MSSE) and the Mean Absolute Scaled Error (MASE). The Mean Absolute Scaled Error (MASE) [@HK06] is calculated as:
$$
  \text{MASE} = \text{mean}(|q_{j}|),
$$
where
$$
  q_{j} = \frac{ e_{j}}
    {\displaystyle\frac{1}{T-m}\sum_{t=m+1}^T |y_{t}-y_{t-m}|},
$$
and $e_{j}$ is the point forecast error for forecast horizon $j$, $m = 7$ (as we have daily seasonal series), $y_t$ is the observation for period $t$, and $T$ is the sample size (the number of observations used for training the forecasting model). The denominator is the mean absolute error of the seasonal naive method in the fitting sample of $T$ observations and is used to scale the error. Smaller MASE values suggest more accurate forecasts. Note that the measure is scale-independent, thus allowing us to average the results across series.

A related measure is MSSE [@hyndman2021forecasting], which uses squared errors rather than absolute errors:
$$
  \text{MSSE} = \text{mean}(q_{j}^2),
$$ {#eq-RMSSE}
where,
$$
  q^2_{j} = \frac{ e^2_{j}}
    {\displaystyle\frac{1}{T-m}\sum_{t=m+1}^T (y_{t}-y_{t-m})^2},
$$
Again, this is scale-independent, and smaller MSSE values suggest more accurate forecasts.

To measure the forecast distribution accuracy, we calculate the Continuous Rank Probability Score [@gneiting2014probabilistic]. It rewards sharpness and penalizes miscalibration, so it measures overall performance of the forecast distribution.
$$
  \text{CRPS} = \text{mean}(p_j),
$$ {#eq-CRPS}
where
$$
  p_j = \int_{-\infty}^{\infty} \left(G_j(x) - F_j(x)\right)^2dx,
$$
where $G_j(x)$ is the forecasted probability distribution function for forecast horizon $j$, and $F_j(x)$ is the true probability distribution function for the same period.

### 2022-11-16 manuscript/main.qmd
Updating sec 3

bibliography: bibliography.bib
execute:
  echo: false
  message: false
  warning: false
pdf-engine: latexmk
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Annals of Emergency Medicine
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

>>>>

bibliography: bibliography.bib
execute:
  echo: false
  message: false
  warning: false
pdf-engine: pdflatex
format:
  elsevier-pdf:
    keep-tex: true
    include-in-header: preamble.tex
    journal:
      name: Annals of Emergency Medicine
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

### 2022-11-16 manuscript/main.tex
Updating sec 3

@@

\begin{keyword}
    forecasting \sep healthcare \sep emergency services \sep forecast
reconciliation \sep hierarchical time series \sep ambulance demand \sep 
    attended incidents
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, boxrule=0pt, frame hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

The dataset used in this study is from a major ambulance service trust
in Great Britain. It contains information relating to the daily number
of attended incidents from 10 October 2015 to 31 July 2019 by nature of
incidents, priority, the health board managing the service and the
control area (or region). Figure Figure~\ref{fig-hierarchy} depicts both
the hierarchical and grouped structure of the data. Figure
Figure~\ref{fig-hierarchy-1} illustrates the nested hierarchical
structure based on control area and health board and Figure
Figure~\ref{fig-hierarchy-2} shows the grouped structure by priority and
the nature of incident.

@@

Table Table~\ref{tbl-hierarchy} also displays the structure of data with
the total number of series at each level. At the top level, we have the
total attended incidents for the country. We can split these total
attended incidents by control area, by health board, by priority or by
nature of incident. There are 3 control areas breakdown by 7 local
health boards. Attended incident data are categorized into 3 priority
classes of red, amber and green. There are also 35 different nature of
incidents such as chest pain, stroke, breathing problem, etc. In total,
across all levels of disaggregation, there are 1530 time series.

@@

Given the total number of time series, direct visual analysis is
infeasible. Therefore, we first compute features of all 1530 time series
and display the strength of trend and weekly seasonality strength in
Figure Figure~\ref{fig-feature}. Each point represents one time series
with the strength of trend in x-axis and the strength of seasonality in
y-axis. It is clear that there are some series showing strong trends
and/or seasonality, corresponding to series at the higher levels of the
hierarchy. The majority of series show low trend and seasonality. These
are time series belonging to the bottom series, series related to the
nature of incidents for a given control, health board and priority
level. Bottom series are dominated by noise with little or no systematic
patterns.

@@

In addition to displaying the trend and seasonality features, we also
visualize few time series at various levels of the aggregation. Figure
Figure~\ref{fig-dataviz2} reveals different information such as trend,
seasonality and noise. For example, some series depict seasonality and
trend, whereas some other series report low volume of attended incidents
and entropy, making them more volatile and difficult to forecast. At the
level on nature of incidents combined with categories of other levels,
there are many series that contain zeros with low counts. As such, the
data set represents a diverse set of daily time series patterns.

@@

\textbf{Naive:} We start with one of the simplest forecasting approaches
used in practice - assuming that in the next few days, everything will
be the same as similar days in the past. This is called ``Naïve''. In
our case, given that we need a distribution of values, we will use a
modified approach, where the empirical distribution of the daily
attended incidents time series is used to forecast the future attended
incidents distribution. We consider the empirical distribution of the
most recent year of historic data on a rolling basis to capture
potential changes in behavior over time.

@@

Despite the popularity and the relevance of automatic \texttt{ETS} in
this study, however it may produce forecasts that are non-integer and
negative. However, the number of attended incidents is an integer and
non-negative. When using \texttt{ETS} , a time series transformation
approach could be used to generate strictly positive forecasts, however
forecasts are still not integer. An alternative is to use forecasting
models that produce integer, non-negative forecasts. in the following
section we present Generalized Linear Models (GLMs) and Poisson
Regression to produce count base forecasts.

\textbf{Generalized Linear Model (GLM): } GLMs are a family of models
developed to extend the concept of linear regression models. They
perform a regression by modeling the response variable as coming from a
particular member of the exponential family, and then transforming the
mean of the response so that the transformed mean is a linear function
of the predictors. One of the models that is frequently used in practice
to generate count forecasts is the Poisson regression. We will consider
forecasting attended incidents using the covariates spline trend, day of
the week dummy variables (from Monday to Sunday), Fourier terms to
capture yearly seasonality, public holidays (1 when is public holiday, 0
otherwise), school holidays (1 when is school holiday, 0 otherwise) and
Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day
(1 when is New Year's Day, 0 otherwise). We fit a Poisson regression
model using the function \texttt{glm()} from the package in R, with the
argument \texttt{family\ =\ poisson} to specify that we wish to fit a
Poisson regression model.

\textbf{Poisson Regression using tscount: } We consider another Poisson
regression model that takes into account serial dependence in addition
to covariates used in the GLM model. To that end, we use
\texttt{tsglm()} function in \emph{tscount} package in R to model the
attended incidents. The logarithmic link function is used to ensure that
the parameter of Poisson distribution is always positive. This model can
be estimated via maximization of the likelihood function based on
Poisson mass function. The regression model captures the short range
serial dependence by including the three order autoregressive terms.

\textbf{Ensemble method:} we also use an ensemble method that combines
forecasts generated from Naive, ETS, GLM and Poisson regression together
to make more accurate forecasts than any individual model.

@@

The data is spitted into training (up until 2018-07-31) and test (from
2018-08-01 to the end) sets, with all model development and
hyper-parameter tuning performed using training data only. The time
series cross validation is performed with a forecast horizon of \(2*42\)
days and advances in 42-day steps. Forecasting performance is evaluated
using both point and probabilistic error measures. Forecast error is
calculated by considering only the last 42 days and not the entire
\(2*42\) days. This corresponds on how forecasts are generated for
planning in practice. Forecasting performance is evaluated using both
point and probabilistic error measures. The point forecast accuracy is
measured via Root Mean Squared Scaled Error (RMSSE) and Mean Absolute
Scaled Error (MASE) that are describes below:

\begin{equation}\protect\hypertarget{eq-RMSSE}{}{
RMSSE = \sqrt{mean(q_{j}^2)},
}\label{eq-RMSSE}\end{equation}

where,

\[
q^2_{j} = \frac{ e^2_{j}}
    {\frac{1}{T-m}\sum_{t=m+1}^T (y_{t}-y_{t-m})^2},
\] \(e_{j}\) is the point forecast error \(j\) and \(m = 1\) for
non-seasonal series and \(m = 7\) for daily seasonal series, \(y_t\) is
the observation for period \(t\) and \(T\) is the sample size
(observations used for training the forecasting model). Smaller RMSSE
values suggest more accurate forecasts. Note that the measure is
scale-independent, thus allowing us to average the results across
series.

Mean Absolute Scaled Error (MASE) is calculated as:

\[
MASE = mean(|q_{j}|),
\]

where, \[
q_{j} = \frac{ e_{j}}
    {\frac{1}{T-m}\sum_{t=m+1}^T |y_{t}-y_{t-m}|}.
\]

The denominator is the mean absolute error of the naive method in the
fitting sample of \(n\) observations and is used to scale the error.

To measure the forecast distribution performance, we calculate the
Continuous Rank Probability Score \citep{gneiting2014probabilistic}. It
rewards sharpness and penalizes miscalibration, so it measures overall
performance.

\begin{equation}\protect\hypertarget{eq-CRPS}{}{
CRPS=\frac{1}{h} \sum_{j=1}^{h} \int_{-\infty}^{\infty} \left(F^f_j(x) - F^0_j(x)\right)^2dx
}\label{eq-CRPS}\end{equation}

where \(F^f_j(x)\) is the forecasted Cumulative Density Function (CDF)
of period \(j\) and \(F^0_j(x)\) is the true CDF of period \(j\).

>>>>

\usepackage{todonotes,mathtools}
\mathtoolsset{showonlyrefs}

@@

\begin{keyword}
    forecasting \sep healthcare \sep emergency services \sep forecast
reconciliation \sep hierarchical time series \sep ambulance demand \sep 
    attended incidents
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, sharp corners, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

The dataset used in this study is from a major ambulance service trust
in Great Britain. It contains information relating to the daily number
of attended incidents from 1 October 2015 to 31 July 2019, disaggregated
by nature of incidents, priority, the health board managing the service
and the control area (or region). Figure~\ref{fig-hierarchy} depicts
both the hierarchical and grouped structure of the data.
Figure~\ref{fig-hierarchy-1} illustrates the nested hierarchical
structure based on control area and health board and
Figure~\ref{fig-hierarchy-2} shows the grouped structure by priority and
the nature of incident.

@@

Table~\ref{tbl-hierarchy} also displays the structure of data with the
total number of series at each level. At the top level, we have the
total attended incidents for the country. We can split these total
attended incidents by control area, by health board, by priority or by
nature of incident. There are 3 control areas breakdown by 7 local
health boards. Attended incident data are categorized into 3 priority
classes of red, amber and green. There are also 35 different nature of
incidents such as chest pain, stroke, breathing problem, etc. In total,
across all levels of disaggregation, there are 1530 time series.

@@

Given the total number of time series, direct visual analysis is
infeasible. Therefore, we first compute features of all 1530 time series
\citep{m3pca} and display the strength of trend and weekly seasonality
strength in Figure~\ref{fig-feature}. Each point represents one time
series with the strength of trend in x-axis and the strength of
seasonality in y-axis. It is clear that there are some series showing
strong trends and/or seasonality, corresponding to series at the higher
levels of the hierarchy. The majority of series show low trend and
seasonality. These are time series belonging to the bottom series,
series related to the nature of incidents for a given control, health
board and priority level. Bottom series are dominated by noise with
little or no systematic patterns.

@@

In addition to displaying the trend and seasonality features, we also
visualize few time series at various levels of the aggregation.
Figure~\ref{fig-dataviz2} reveals different information such as trend,
seasonality and noise. For example, some series depict seasonality and
trend, whereas some other series report low volume of attended incidents
and entropy, making them more volatile and difficult to forecast. At the
level on nature of incidents combined with categories of other levels,
there are many series that contain zeros with low counts. As such, the
data set represents a diverse set of daily time series patterns.

@@

\textbf{Naive:} We start with a simple forecasting approach, assuming
that the future days will be similar to past days. We use the empirical
distribution of the past daily attended incidents to create the forecast
distribution of future attended incidents. We consider the empirical
distribution of the most recent year of historic data on a rolling basis
to capture potential changes in behavior over
time.\todo{Actually we use all the data.}

@@

Despite the popularity and the relevance of automatic \texttt{ETS} in
this study, however it may produce forecast distributions that are
non-integer and include negative values, despite the number of attended
incidents being integer and non-negative. When using \texttt{ETS}, a
time series transformation approach could be used to generate strictly
positive forecasts, although forecast distributions will still be
non-integer. An alternative is to use forecasting models that produce
integer, non-negative forecasts. in the following section we present
Generalized Linear Models (GLMs) and Poisson Regression to produce count
base forecasts.

\textbf{Generalized Linear Model (GLM):} GLMs are a family of models
developed to extend the concept of linear regression models. They
perform a regression by modeling the response variable as coming from a
particular member of the exponential family, and then transforming the
mean of the response so that the transformed mean is a linear function
of the predictors. One of the models that is frequently used in practice
to generate count forecasts is the Poisson regression. We will consider
forecasting attended incidents using the covariates spline trend, day of
the week dummy variables (from Monday to Sunday), Fourier terms to
capture yearly seasonality, public holidays (1 when is public holiday, 0
otherwise), school holidays (1 when is school holiday, 0 otherwise) and
Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day
(1 when is New Year's Day, 0 otherwise). We fit a Poisson regression
model using the function \texttt{glm()} from the package in R, with the
argument \texttt{family\ =\ poisson} to specify that we wish to fit a
Poisson regression model.

\textbf{Poisson Regression using tscount:} We consider another Poisson
regression model that takes into account serial dependence in addition
to covariates used in the GLM model. To that end, we use
\texttt{tsglm()} function in \emph{tscount} package in R to model the
attended incidents. The logarithmic link function is used to ensure that
the parameter of Poisson distribution is always positive. This model can
be estimated via maximization of the likelihood function based on
Poisson mass function. The regression model captures the short range
serial dependence by including the three order autoregressive terms.

\textbf{Ensemble method:} we also use an ensemble method that combines
forecasts generated from Naive, ETS, GLM and Poisson regression to form
a mixture distribution \citep{combinations}.

@@

To evaluate the performance of the various forecasting approaches, we
split the data into a series of ten training and test sets. We use a
time series cross-validation approach \citep{hyndman2021forecasting},
with a forecast horizon of 84 days, and each training set expanding in
42-day steps. The first training set uses all data up to 2018-04-25, and
the first test set uses the 84 days beginning 2018-04-26. The second
training set uses all data up to 2018-06-06, with the second test set
using the following 84 days. The largest training set ends on
2019-05-09, with the test set ending on 2019-07-31. Model development
and hyper-parameter tuning is performed using the training data only.
Forecasting performance is evaluated using both point and probabilistic
error measures. While we compute forecast errors for the entire 12
weeks, we are most interested in the last 42 days of each test set,
because that corresponds to how forecasts are generated for planning in
practice. Forecasting performance is evaluated using both point and
probabilistic error measures.

Point forecast accuracy is measured via the Mean Squared Scaled Error
(MSSE) and the Mean Absolute Scaled Error (MASE). The Mean Absolute
Scaled Error (MASE) \citep{HK06} is calculated as: \[
  \text{MASE} = \text{mean}(|q_{j}|),
\] where \[
  q_{j} = \frac{ e_{j}}
    {\displaystyle\frac{1}{T-m}\sum_{t=m+1}^T |y_{t}-y_{t-m}|},
\] and \(e_{j}\) is the point forecast error for forecast horizon \(j\),
\(m = 7\) (as we have daily seasonal series), \(y_t\) is the observation
for period \(t\), and \(T\) is the sample size (the number of
observations used for training the forecasting model). The denominator
is the mean absolute error of the seasonal naive method in the fitting
sample of \(T\) observations and is used to scale the error. Smaller
MASE values suggest more accurate forecasts. Note that the measure is
scale-independent, thus allowing us to average the results across
series.

A related measure is MSSE \citep{hyndman2021forecasting}, which uses
squared errors rather than absolute errors:
\begin{equation}\protect\hypertarget{eq-RMSSE}{}{
  \text{MSSE} = \text{mean}(q_{j}^2),
}\label{eq-RMSSE}\end{equation} where, \[
  q^2_{j} = \frac{ e^2_{j}}
    {\displaystyle\frac{1}{T-m}\sum_{t=m+1}^T (y_{t}-y_{t-m})^2},
\] Again, this is scale-independent, and smaller MSSE values suggest
more accurate forecasts.

To measure the forecast distribution accuracy, we calculate the
Continuous Rank Probability Score \citep{gneiting2014probabilistic}. It
rewards sharpness and penalizes miscalibration, so it measures overall
performance of the forecast distribution.
\begin{equation}\protect\hypertarget{eq-CRPS}{}{
  \text{CRPS} = \text{mean}(p_j),
}\label{eq-CRPS}\end{equation} where \[
  p_j = \int_{-\infty}^{\infty} \left(G_j(x) - F_j(x)\right)^2dx,
\] where \(G_j(x)\) is the forecasted probability distribution function
for forecast horizon \(j\), and \(F_j(x)\) is the true probability
distribution function for the same period.
